\LARGE \bf Planning with Attitude

### 2020-10-10 paper/main.tex
Updates from Overleaf

    \subsection{Results}
    \begin{figure}
        \centering
        \includegraphics[width=\columnwidth, height=5cm]{figures/wahba_convergence.tikz}
        \caption{Convergence comparison for Wahba's problem. By performing Newton's method
        on the error quaternion and applying the result to the full quaternion we achieve
        quadratic convergence, whereas the more na\"ive approach doesn't converge to zero
        error.}
        \label{fig:wahba_convergence}
    \end{figure}

>>>>

    \subsection{Results}

    As visible in figure \ref{fig:wahba_convergence}, the original Newton's method makes progress early on in the iterations, but stops making progress as the normalization errors grow. The modified Newton's method, that applies the newton step as a rotation instead of an addition, is able to converge to floating point accuracy.

    \begin{figure}[H]
        \centering
        \includegraphics[width=\columnwidth, height=5cm]{figures/wahba_convergence.tikz}
        \caption{Convergence comparison for Wahba's problem. By performing Newton's method
        on the error quaternion and applying the result to the full quaternion we achieve
        quadratic convergence, whereas the more na\"ive approach doesn't converge to zero
        error.}
        \label{fig:wahba_convergence}
    \end{figure}
    % \begin{figure}[H]
    %     \centering
    %     \includegraphics[width=\columnwidth, height=5cm]{figures/kevins_plots/convergence_plot.tikz}
    %     \caption{Convergence comparison for Wahba's problem. By performing Newton's method
    %     on the error quaternion and applying the result to the full quaternion we achieve
    %     quadratic convergence, whereas the more na\"ive approach doesn't converge to zero
    %     error.}
    %     \label{fig:wahba_convergence}
    % \end{figure}
